### 2013-06-16 doc/icml2013/evaluation.tex
Added new plots

\begin{figure}[t]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.png}
  \caption{Histogram over recovery errors between the three algorithms when $b = 1, d = 4, k = 3, n = 500,000$.}
  \label{fig:hist}
\end{figure}

\begin{figure*}[p]
  \centering
  \subfigure[Spectral, Spectral+EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.png}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.png}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{Visualization of the parameters estimated by Spectral Experts versus EM.
  (a) The dashed lines denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to further improve the solution (solid lines).
  (b) The dotted lines show different local optima found by EM.}
  \label{fig:curves}
\end{figure*}

@@

\begin{figure*}[tbhp]
  \centering
  \subfigure[Well-specified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.png}
  }
    \hspace{-2em}
  \subfigure[Misspecified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.png}
  }
  \caption{Learning curves: parameter error as a function of the number of samples $n$ ($b = 1, d = 5, k = 3$).}
  \label{fig:vs-n}
\end{figure*}

>>>>

\begin{figure}[t]
  \centering
  %\includegraphics[width=0.50\textwidth]{figures/hist.png}
  \includegraphics[width=0.50\textwidth]{figures/EM-Spectral-Spectral+EM-hist.pdf}
  \caption{Histogram over recovery errors between the three algorithms when $b = 1, d = 4, k = 3, n = 500,000$.}
  \label{fig:hist}
\end{figure}

\begin{figure*}[p]
  \centering
  \subfigure[Spectral, Spectral+EM]{
    %\includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.png}}
    \includegraphics[width=0.50\textwidth]{figures/Spectral-Spectral+EM-1833.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    %\includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.png}}
    \includegraphics[width=0.50\textwidth]{figures/EM-1833.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{Visualization of the parameters estimated by Spectral Experts versus EM.
  (a) The dashed lines denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to further improve the solution (solid lines).
  (b) The dotted lines show different local optima found by EM.}
  \label{fig:curves}
\end{figure*}

@@

\begin{figure*}[tbhp]
  \centering
  \subfigure[Well-specified data]{
    %\includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.png}
    \includegraphics[width=0.50\textwidth]{figures/vs-n-1833.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n-1833-rm.pdf}
    %\includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.png}
  }
  \caption{Learning curves: parameter error as a function of the number of samples $n$ ($b = 1, d = 5, k = 3$).}
  \label{fig:vs-n}
\end{figure*}
